\pkg{disaggregation}: An \proglang{R} Package for Bayesian Spatial Disaggregation Modelling

### 2020-02-24 article.Rnw

%
<<kintroptions, echo=FALSE>>=
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  fig.width = 6,
  fig.height = 4,
  fig.pos = 'H'
)
@
%

>>>>

%
<<kintroptions, echo=FALSE>>=
knitr::knit_hooks$set(render_sweave())
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  fig.width = 6,
  fig.height = 4,
  fig.pos = 'H',
  prompt=TRUE
)
options(replace.assign=TRUE, width=90, prompt="R> ")
@
%
